A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-09-25 manuscript.Rmd
thank Michèle Nuijten closes #68
also mention figshare as doi provider see #60

authornote: |
   We are grateful to Julia Delius for her helpful assistance in language and style editing. We thank the reviewers and all contributors of our GitHub repository for helpful feedback on the paper. This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompanying GitHub repository: [https://github.com/aaronpeikert/reproducible-research/](https://github.com/aaronpeikert/reproducible-research/). This document is based on the commit identified by hash `"`r system2("git", "rev-parse --short HEAD", stdout = TRUE)`"`. To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the GitHub repository of our paper at [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).

@@

GitHub allows you to archive and label a specific version of your repository in the form of a release. A release tags a particular commit with an arbitrary label, e.g., as "submission,"[^sub] "preprint," or "published," and archives also "binary" products of your code, e.g. the resulting pdf of the manuscript or the docker image (see [Containerization]). From such a release [zenodo.org](https://zenodo.org) can create a DOI, making it easier to reference it (see this [GitHub Guide](https://guides.github.com/activities/citable-code/)[^doi]).

>>>>

authornote: |
   We are grateful to Julia Delius for her helpful assistance in language and style editing. We thank the anonymous reviewer and Michèle Nuijten, and all contributors of our GitHub repository for helpful feedback on the paper. This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompanying GitHub repository: [https://github.com/aaronpeikert/reproducible-research/](https://github.com/aaronpeikert/reproducible-research/). This document is based on the commit identified by hash `"`r system2("git", "rev-parse --short HEAD", stdout = TRUE)`"`. To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the GitHub repository of our paper at [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).

@@

GitHub allows you to archive and label a specific version of your repository in the form of a release. A release tags a particular commit with an arbitrary label, e.g., as "submission,"[^sub] "preprint," or "published," and archives also "binary" products of your code, e.g. the resulting pdf of the manuscript or the docker image (see [Containerization]). From such a release [zenodo.org](https://zenodo.org) or [figshare.com](https://figshare.com) can create a DOI, making it easier to reference it (see this [GitHub Guide](https://guides.github.com/activities/citable-code/)[^doi]).
